\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{hyperref}

% Page geometry
\geometry{margin=1in}

% Colors
\definecolor{primaryblue}{RGB}{0,123,255}
\definecolor{secondarygreen}{RGB}{40,167,69}
\definecolor{lightgray}{RGB}{248,249,250}
\definecolor{darkgray}{RGB}{52,58,64}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=primaryblue,
    urlcolor=primaryblue,
}

% Custom title formatting
\titleformat{\section}
{\Large\bfseries\color{primaryblue}}
{\thesection}{1em}{}

\titleformat{\subsection}
{\large\bfseries\color{secondarygreen}}
{\thesubsection}{1em}{}

\pagestyle{empty} % No page numbers or headers

\begin{document}

% Title page
\begin{titlepage}
    \centering
    \vspace*{4cm}
    
    {\Huge\bfseries\color{primaryblue} PurrfectMatch}\\[0.5cm]
    {\Large\color{secondarygreen} Technology Stack Overview}\\[3cm]
    
    \begin{tcolorbox}[colback=lightgray, colframe=primaryblue, width=0.9\textwidth]
        \centering
        \textbf{A summary of the core technologies, frameworks, and libraries used in the PurrfectMatch pet adoption platform.}
    \end{tcolorbox}
    
    \vfill
    
    {\Large \today}
\end{titlepage}

\newpage

\section*{Technology Stack}

PurrfectMatch is a full-stack application built on a modern, robust, and scalable technology stack. The architecture is designed to be maintainable and testable, following Clean Architecture principles.

\subsection*{Backend Technologies}

The backend is built on the .NET ecosystem, providing a high-performance and secure foundation for the API and business logic.

\begin{tcolorbox}[colback=lightgray, colframe=secondarygreen, title=Core Backend Stack]
    \begin{itemize}[leftmargin=*]
        \item \textbf{.NET 8}: The core framework for building the application.
        \item \textbf{ASP.NET Core 8}: Used for building the RESTful Web API.
        \item \textbf{Entity Framework Core 8}: The object-relational mapper (ORM) for data access.
        \item \textbf{Microsoft SQL Server}: The primary relational database.
        \item \textbf{ASP.NET Core Identity}: For handling user authentication and authorization.
    \end{itemize}
\end{tcolorbox}

\subsection*{Frontend Technologies}

The frontend is a modern single-page application (SPA) built with React and TypeScript, ensuring a type-safe and component-based UI.

\begin{tcolorbox}[colback=lightgray, colframe=secondarygreen, title=Core Frontend Stack]
    \begin{itemize}[leftmargin=*]
        \item \textbf{React 19}: The JavaScript library for building the user interface.
        \item \textbf{TypeScript 5.7}: Provides static typing for JavaScript.
        \item \textbf{Vite}: The build tool and development server for the frontend.
        \item \textbf{Material-UI (MUI)}: A comprehensive library of UI components.
        \item \textbf{Redux Toolkit}: For predictable and centralized state management.
        \item \textbf{React Router}: For client-side routing and navigation.
    \end{itemize}
\end{tcolorbox}

\newpage

\subsection*{Real-time Communication and Payments}

Specialized services are integrated to handle real-time features and secure financial transactions.

\begin{tcolorbox}[colback=lightgray, colframe=primaryblue, title=Key Integrations]
    \begin{itemize}[leftmargin=*]
        \item \textbf{ASP.NET Core SignalR}: Enables real-time, bidirectional communication between the server and clients for features like notifications and live updates.
        \item \textbf{Stripe}: Provides a secure and PCI-compliant platform for processing donations and other payments. The integration uses Stripe.js on the frontend and the Stripe.NET library on the backend.
    \end{itemize}
\end{tcolorbox}

\subsection*{Cloud and DevOps}

The application is designed for the cloud, utilizing Azure services for storage and a CI/CD pipeline for automated builds and deployments.

\begin{tcolorbox}[colback=lightgray, colframe=primaryblue, title=Cloud Infrastructure]
    \begin{itemize}[leftmargin=*]
        \item \textbf{Azure Blob Storage}: Used for storing user-uploaded content such as pet photos and documents.
        \item \textbf{Azure DevOps}: Implements the CI/CD pipeline for automating the build, test, and deployment processes.
    \end{itemize}
\end{tcolorbox}

\subsection*{Supporting Libraries and Tools}

A selection of powerful libraries are used to support development, testing, and application functionality.

\begin{tcolorbox}[colback=lightgray, colframe=darkgray, title=Development and Tooling]
    \begin{itemize}[leftmargin=*]
        \item \textbf{AutoMapper}: For object-to-object mapping between layers.
        \item \textbf{Serilog}: For structured and flexible logging.
        \item \textbf{Swashbuckle}: To generate OpenAPI (Swagger) documentation for the API.
        \item \textbf{xUnit}: The testing framework for .NET.
        \item \textbf{Moq}: A mocking library for creating test doubles.
        \item \textbf{ESLint}: For linting TypeScript and JavaScript code.
    \end{itemize}
\end{tcolorbox}

\end{document}
